Main Analyses

### 2016-05-05 Rmd/figures.Rmd
Full paper revisions: main manuscript, fully revised, with edits and additions to SI methods and results.  New figure created (figures.Rmd), slight edit of loose code on main-analysis.Rmd

setwd("~/Dropbox/publications/zambiaToff/private/zambiaToff/")
p_root <- getwd()
p_demand <- fp(p_root, "external/input_devel/demand/")
p_mod <- fp(p_root, "agroEcoTradeoff")
p_moddat <- fp(p_mod, "external/data/ZA")
p_figures <- full_path(p_root, "paper/figures/")
p_other <- fp(p_root, "external/input_devel/other/")
p_bd <- fp(p_root, "external/input_devel/biodiversity")
# p_roads <- fp(p_root, "external/input_devel/roads")
# p_roads2 <- paste0("/Users/lestes/Dropbox/data/zari/infrastructure/zambia/", 
#                    "rda_dump/Final Shape files RDA/")
p_out <- fp(p_mod, "external/output")
```

@@

## Figures

How reconcilable are the different land use interests, and what would be the impacts of each?

I am using the two crops combined approach because there is little overlap between the two.

### Figure 1
```{r, eval = FALSE}
load(fp(p_out, "mainresults2802.rda"))

@@

# Plot setup
m1 <- do.call(cbind, lapply(1:4, function(x) matrix(rep(x, 35), 5, 7)))
m2 <- do.call(cbind, lapply(c(5, 8, 11, 14), function(x) {
  a <- matrix(rep(x, 16), 4, 4)
  b <- matrix(rep(x + 1, 6), 2, 3)
  cbind(a, rbind(b, b + 1))
}))

# m2 <- matrix(rep(5, 20), 4, 5)
# m3 <- do.call(cbind, lapply(6:12, function(x) matrix(rep(x, 12), 4, 3)))
# lmat <- rbind(m1, cbind(rep(5, 4), m2, m3, rep(13, 4)))
lmat <- rbind(m1, m2)

ylabs <- c(expression(paste("Converted area (", km^2, " X ", 10^-5, ")")), 
           "Carbon loss (Mt)", #"Priority", 
           expression(paste("Biodiversity Index X ", 10^-5)),
           expression(paste("Truck hours X ", 10^-5)))#,
           # "Intactness", expression(paste("FR converted (ha"^2, ")")))
# yscale <- c(1, 10^5, 1, 100000, 1, 1, 1, 1)
yscale <- rep(100000, 4)#, 10000, 10000)#, 1, 1, 1)
ftits <- list("Maximize Yields", "Minimize Carbon Loss", 
              "Minimize Biodiversity Loss", "Minimize Travel Cost")
# leg <- c("Converted")
yaxes <- list(seq(0, 16, 2), seq(0, 1200, 100), seq(0, 9, 1), 
              seq(0, 35, 5))#,               
              # seq(0, 1200, 100), #seq(0, 0.12, 0.02)), 
              #seq(0, 1, 0.1), seq(0, 6500, 500))
# bcols <- c(list(c(cols_tr[1], cols_tr[2], cols_tr[1], cols_tr[2], 
#                   cols_tr[3])), lapply(1:7, function(x) rep("black", 4)))

@@

### Figures 2 & 3 (probably supplemental)
Deprecated
```{r, eval = FALSE}
# individual maps
# png(full_path(p_figures, "all-4-maps.png"), height = 7, width = 7, 
#      units = "in", res = 300)
# par(mfrow = c(2, 2))#, oma = c(0, 0, 0, 2))
# ftitles <- c("Yield", "Carbon", "Biodiversity", "Cost")
# legp <- c(TRUE, rep(FALSE, 3))
# for(i in 1:4) {
#   dtr <- calc(pure_r[[i]][[1:2]] * c(1, 2), sum)
#   imp_plot2(dtr, impacts = i1, fpath = p_figures, fnm = "all-4-maps", 
#             cexscale = 0.6, ftitle = ftitles[i], crops = c("maize", "soy"), 
#             stats = FALSE, hold = TRUE, legend = legp[i], marg = c(0, 0, 2, 0))
# }
# dev.off()

@@

### Figures 4 (main) and 5 (probably supplemental)

@@

cols_tr <- c(rgb(1, 0, 0), rgb(0, 0, 1), rgb(0, 0.75, 1), rgb(1, 0.75, 0))
# sctab <- do.call(rbind, scens) * 100
cx <- 0.7
# lcols <- c("black", "red", "blue")
# imp_pct[, {
#   png(fp(p_figures, "weight_impact.png"), height = 4, width = 4, 
#       units = "in", res = 300)
#   par(mgp = c(2, 0.75, 0), mar = c(3, 3, 1, 1))
#   plot(conv_area, tot_C, type = "l", xlab = "", ylab = "", #xaxt = "n", 
#   lines(conv_area, int_prior, col = "red")
#   lines(conv_area, mu_cost, col = "blue")
#   axis(1, at = seq(2, 12, 1), cex = cx, cex.axis = cx, line = -0.25, 
#        tcl = -0.2, mgp = c(1, 0.25, 0))
#   axis(2, at = seq(0, 60, 5), las = 2, cex = cx, cex.axis = cx, line = -0.25, 
#        tcl = -0.15, mgp = c(1, 0.25, 0))
#   mtext("% land savings", side = 1, line = 1, cex = cx)
#   mtext("% Carbon/Biodiv/Cost savings", side = 2, line = 1, cex = cx)
#   inms <- c("tot_C", "int_prior", "mu_cost")
#   for(i in 1:length(inms)) {
#     text(conv_area[-1], get(inms[i])[-1], labels = sctab[-1, i + 1], 
#          cex = cx * 0.8, pos = 3, offset = 0.2, col = lcols[i])
#     text(conv_area[1] + 0.1, i, labels = 0, cex = cx * 0.8, pos = 3, 
#          offset = i * 0.15 - 0.2, col = lcols[i])
#   }
#   legend("bottomleft", legend = c("Carbon", "Biodiv", "Cost"), cex = cx,
#          text.col = lcols, col = lcols, bty = "n", lty = 1)
imp_pct[, {
  png(fp(p_figures, "weight_impact5.png"), height = 4, width = 4, 
      units = "in", res = 300)
  plot(xwgts, conv_areap, type = "l", xlab = "", ylab = "", axes = FALSE, 
       ylim = c(0, 55), col = cols_tr[1])
  lines(xwgts, tot_Cp, col = cols_tr[2])
  lines(xwgts, cons_totp, col = cols_tr[3])
  lines(xwgts, tot_costp, col = cols_tr[4])
  axis(1, at = xwgts, labels = seq(0, 90, 10), cex = cx, cex.axis = cx, 
       line = -0.25, tcl = -0.2, mgp = c(1, 0.25, 0))
  axis(2, at = seq(0, 55, 5), las = 2, cex = cx, cex.axis = cx, line = -0.25, 
       tcl = -0.15, mgp = c(1, 0.25, 0))
  mtext("% Weight taken from Yield and divided", side = 1, line = 1, cex = cx)
  mtext("equally between Carbon & Biodiversity", side = 1, line = 1.75, 
        cex = cx)
  mtext("% Avoided Cost", side = 2, line = 1, cex = cx)
  legend("bottomright", 
         legend = c("Yield", "Carbon", "Biodiversity", "Travel cost"), 
         cex = cx, text.col = cols_tr, col = cols_tr, bty = "n", lty = 1, 
         inset = c(0, 0.25, 0, 0))
  dev.off()
}]

# fnames <- fp(fp(p_out, ybdc$both$bcode), 
#              imp_sorter(fp(p_out, ybdc$both$bcode), inds = pind))
# scens_r <- lapply(fnames, function(x) {  # x <- pind[[1]]
#   print(x)
#   DT <- cbind(fread(x), basedt[, .(x, y, convertible)])
#   DTr <- dt_to_raster(DT, CRSobj)
# scens_rs2 <- lapply(scens_r, function(x) calc(stack(x[[1:2]]), sum))
# names(scens_rs2) <- paste0("w", 1:length(scens_rs2))
# pms2b <- do.call(rbind.data.frame, lapply(2:6, function(x) {
#   a <- rep(0, 6)
#   a[c(1, x)] <- 1
#   a
# }))
# colnames(pms2b) <- paste0("Var", 1:ncol(pms2b))
# pms2b$cl <- c("W010", "W020", "W030", "W040", "W050")
# rownames(pms2b) <- 1:5
# # pairwise overlaps
# scens_over <- lapply(1:nrow(pms2b), function(x) {  # apply logic tests
#   calc(stack(scens_rs2[which(pms2b[x, ] == 1)]), sum)
# names(scens_over) <- pms2b$cl
# # Jaccard Index of overlaps
# scens_over_a <- sapply(1:length(scens_over), function(x) { # x <- 4
#     r <- scens_over[[x]] == y
#     round(cellStats(r * pure_r[[1]]$convertible, sum), 1)
# pms2b$JS <- round(scens_over_a[2, ] / colSums(scens_over_a), 3)
# scenover_nn <- lapply(1:nrow(pms2b), function(x) {  # apply logic tests; x = 4
#   print(x)
#   ind <- which(pms2b[x, 1:6] == 1)
#   rl <- scens_rs2[ind]
# pms2b$NND <- round(sapply(scenover_nn, function(x) mean(x$dist))) / 1000
# cols_tr <- c(rgb(1, 0, 0), rgb(0, 0, 1), rgb(0, 0.75, 1), rgb(1, 0.75, 0))
# # plot(scens_rs2[[1]] + scens_rs2[[2]])
# # check
# # round(sapply(scens_rs2, function(x) {
# #   cellStats(x * scens_r[[1]]$convertible * 100, sum)
# # }))
# # cstats$conv_area
# # pms <- list(c(1, 2), c(1, 3), c(1, 4), c(1, 5))
# # pms <- expand.grid(rep(list(0:1), 5))[-1, ]  # logic grid
# # rasters showing overlap as weight is progressively put on C and BD
# scens_over2 <- lapply(2:6, function(x) scens_rs2[[1]] + scens_rs2[[x]] * 2)
# # # overlap areas
# # scens_over_a <- sapply(1:length(scens_over), function(x) { # x <- 4
# #   sapply(1:3, function(y) {  # y <- 3
# #     r <- scens_over[[x]] == y
# #     # plot(r)
# #     round(cellStats(r * scens_r[[1]]$convertible, sum), 1)
# # colSums(scens_over_a[c(2, 3), ])
# # over_cols <- sapply(seq(0, 0.4, 0.1), function(x) rgb(1 - x, 0, x))
# # par(mar = c(0, 0, 0, 0))
# # plot(1:3, pch = 20, col = rgb(1, 0, 1))
# # cols <- c(rgb(1, 0, 0), rgb(0, 0, 1), rgb(0.75, 0, 0.75))
# # cols <- c("red", "blue", "gold")
# bluecols <- sapply(c(1, 0.75, 0.5, 0.25, 0), function(x) rgb(0, x, 1))
# bluecols[5] <- rgb(0.4, 0, 1)
# cols <- sapply(1:length(bluecols), function(x) c("red", bluecols[x], "gold"))
# plot(1:ncol(cols), pch = 20, col = cols[2, ], cex = 20)
# ftits <- list("Y 90% C 5% Biod 5% Cost 0%",
#               "Y 80% C 10% Biod 10% Cost 0%",
#               "Y 70% C 15% Biod 15% Cost 0%",
#               "Y 60% C 20% Biod 20% Cost 0%", 
#               "Y 50% C 25% Biod 25% Cost 0%")
# leg <- c("Y", "YCBd", "Y + YCBd")
# tiff(fp(p_figures, "changing_weights2.tif"), height = 3.5, width = 7, 
# par(mfrow = c(2, 3), oma = c(0, 0, 0, 1))
# for(i in 1:5) { # i <- 1
#   imp_plot2(scens_over2[[i]], impacts = i1, fpath = p_figures, fnm = "bob",
#             crops = leg, ftitle = ftits[[i]], col = cols[, i], 
#             marg = c(0, 0, 1, 0), titline = 0)
# par(mar = c(3, 3, 1, 0))
#      plot(NND, JS, col = cols[2, ], pch = 16, cex = 1.5, 
#           axes = FALSE, xlab = "", ylab = "", ylim = c(0, 0.4), 
#           xlim = c(0, 180))
#      points(NND, JS, col = cols[[1]][1], pch = 20, cex = 1)
#      axis(1, at = seq(0, 180, 20), cex.axis = 0.6, las = 2, mgp = mgp, 
# #   # barplot
# #   par(mar = c(5, 4, 3, 3))
# #   overl <- scens_over_a[1:3, i][c(1, 3, 2)]
# #   bp <- barplot(overl, las = 2, ylim = c(0, 12000),  
# #                 col = cols[c(1, 3, 2)], mgp = c(1.5, 0.25, 0), tcl = -0.2, 
# #                 ylab = expression(km^2), cex.axis = 0.6, cex.lab = 0.7)
# #   axis(side = 1, at = bp, labels = leg, las = 2, 
# #        mgp = c(1, 0.25, 0), tcl = -0.2, cex.axis = 0.6)
# # }
# # dev.off()

@@

### Figure 6

@@

# do sum factoring in overlaps 
# sapply(tores_over_r, function(x) {
#   round(cellStats(x * scens_r[[1]]$convertible, sum), 1)
# })

# cols_tr <- c(rgb(1, 0, 0), rgb(1, 0.75, 0), rgb(0, 0, 1), rgb(0, 0.75, 1))
# cols_tr <- c(rgb(1, 0, 0), rgb(0, 0, 1), rgb(0, 0.75, 1), rgb(1, 0.5, 0), 
#              "gold")#rgb(1, 1, 0))
# plot(1:length(cols_tr), cex = 3, pch = 20, col = cols_tr)

# layout matrix
# m1 <- do.call(cbind, lapply(1:5, function(x) matrix(rep(x, 45), 6, 9)))
# m2 <- matrix(rep(6, 36), 4, 9)
# m3 <- do.call(cbind, lapply(7:13, function(x) matrix(rep(x, 20), 4, 5)))
# f1 <- lapply(14:15, function(x) cbind(rep(x, 4), rep(x, 4)))
# lmat <- rbind(m1, cbind(m2, m3, rep(14, 4)))
# lmat <- rbind(m1, m3)
# cbind(m2, m3)

# # plot(1:10, ylab = ylabs[2])
# # ylabs <- c("Jaccard Index", 
# ylabs <- c(expression(paste("Conv. area (", 10^5, " ", km^2, ")")), 
#            "Hours", "C loss (Mt)", "Priority", "Intactness/priority",
#            "Intactness", expression(paste("FR converted (ha"^2, ")")))
# # yscale <- c(1, 10^5, 1, 100000, 1, 1, 1, 1)
# yscale <- c(10^5, 1, 100000, 1, 1, 1, 1)

@@

# # yaxes <- list(seq(0, 0.8, 0.1), seq(0, 14, 2), seq(0, 2.5, 0.5), 
# maxes <- sapply(c(2, 5, 3, 7:9, 4), function(j) minmaxstats[[j]][2])
# mins <- sapply(c(2, 5, 3, 7:9, 4), function(j) minmaxstats[[j]][1])
# ymaxes <- maxes / yscale
# ymins <- mins / yscale
# yaxes <- list(seq(0, 15, 3), 0:7, seq(0, 1100, 100), seq(0, 0.15, 0.05), 
#               seq(0, 0.6, 0.1), seq(0, 1, 0.1), seq(0, 7000, 1000))
#

@@

# # bcols <- c(list(c(cols_tr[1], cols_tr[1], cols_tr[2], cols_tr[1], cols_tr[2],
# pms2b$icol <- cols_tr[c(1, 1, 2, 1, 2, 3, 1, 2, 3, 4)]  # circle inner
# pms2b$ocol <- cols_tr[c(2, 3, 3, 4, 4, 4, 5, 5, 5, 5)]  # circle outer
# 
# tiff(fp(p_figures, "objective-subjective_weights.tif"), height = 2.5, width = 7,      units = "in", res = 300)
# l <- layout(mat = lmat)
# layout.show(l)

# # map plots
# for(i in 1:length(toresr)) { # i <- 1
#   # map
# #   par(mar = rep(0, 4))
# #   plot(zambia, col = cols_tr[i])
#   imp_plot2(toresr[[i]], impacts = i1, fpath = p_figures, fnm = "bob",
#             crops = leg, ftitle = ftits[[i]], col = cols_tr[[i]], 
#             legend = TRUE, hold = TRUE, stats = FALSE, cexscale = 0.3, 
#             marg = rep(0, 4), inset = c(0.1, 0.1, 0, 0))
# }  
# 
# # impact plots
# mgp <- c(0.9, 0.25, 0)
# par(mar = c(3, 3, 0, 3))
# with(pms2b, {
#      plot(NND, JS, col = pms2b$icol, pch = 16, cex = 0.8, 
#           axes = FALSE, xlab = "", ylab = "", ylim = c(0, 0.6), 
#           xlim = c(0, 25))
#      points(NND, JS, col = pms2b$ocol, pch = 20, cex = 0.5)
#      axis(1, at = seq(0, 25, 5), cex.axis = 0.5, las = 2, mgp = mgp, 
#           tcl = -0.2)
#      axis(2, at = seq(0, 0.6, 0.1), cex.axis = 0.5, las = 2, mgp = mgp, 
#           tcl = -0.2)
#      mtext(text = "NN Distance (km)", side = 1, line = 0.5, cex = 0.4)
#      mtext(text = "Jaccard Index", side = 2, line = 1, cex = 0.4)
# })
# par(mar = c(3, 3, 0, 0))
# mgp <- c(1.3, 0.25, 0)
# for(i in 1:7) { # i <- 1
#   v <- impsr[[i]] / yscale[i]
#   b <- barplot(impsr[[i]] / yscale[i], las = 2,  col = cols_tr, 
#                mgp = mgp, tcl = -0.2, yaxt = "n", 
#                ylim = range(yaxes[[i]]), ylab = ylabs[i], cex.axis = 0.4,
#                cex.lab = 0.55)
#   lines(c(-1, 7), rep(ymins[i], 2), lwd = 1, col = "grey50")
#   lines(c(-1, 7), rep(ymaxes[i], 2), lwd = 1)
#   axis(2, at = yaxes[[i]], cex.axis = 0.5, las = 2, mgp = mgp, 
#        tcl = -0.2)
# }
# dev.off()

@@

### Overlap with Farm Blocks
```{r, eval = FALSE}
# Calculate area of overlaps between farmblocks and 
Y <- calc(mzsoytor, sum)
yfbr <- Y + fbr * 2
eqfbr <- toresr$eqwt + fbr * 2
fbrlist <- list(yfbr, eqfbr)

fb_over_a <- sapply(1:2, function(x) { # x <- 4
  sapply(1:3, function(y) {  # y <- 3
    r <- fbrlist[[x]] == y
    round(cellStats(r * pure_r[[1]]$convertible, sum), 1)
  })
})
fb_sim <- fb_over_a[3, ] / colSums(fb_over_a)

@@

@@

```{r, eval = FALSE}

@@

>>>>

setwd("~/Dropbox/publications/zambiaToff/private/zambiaToff/")
p_root <- getwd()
p_demand <- fp(p_root, "external/input_devel/demand/")
p_mod <- fp(p_root, "agroEcoTradeoff")
p_moddat <- fp(p_mod, "external/data/ZA")
p_figures <- full_path(p_root, "paper/figures/")
p_other <- fp(p_root, "external/input_devel/other/")
p_bd <- fp(p_root, "external/input_devel/biodiversity")
# p_roads <- fp(p_root, "external/input_devel/roads")
# p_roads2 <- paste0("/Users/lestes/Dropbox/data/zari/infrastructure/zambia/", 
#                    "rda_dump/Final Shape files RDA/")
p_out <- fp(p_mod, "external/output")

for(i in c("selected_impacts.R", "imp_sorter.R", "imp_plot2.R")) {
  source(fp(p_root, paste0("R/", i)))
}
```

@@

## Figures
### Figure 1 - pure objectives
```{r, eval = FALSE}
load(fp(p_out, "mainresults2802.rda"))

@@

# Plot setup
m1 <- do.call(cbind, lapply(1:4, function(x) matrix(rep(x, 35), 5, 7)))
m2 <- do.call(cbind, lapply(c(5, 8, 11, 14), function(x) {
  a <- matrix(rep(x, 16), 4, 4)
  b <- matrix(rep(x + 1, 6), 2, 3)
  cbind(a, rbind(b, b + 1))
}))
lmat <- rbind(m1, m2)

ylabs <- c(expression(paste("Converted area (", km^2, " X ", 10^-5, ")")), 
           "Carbon loss (Mt)", #"Priority", 
           expression(paste("Biodiversity Index X ", 10^-5)),
           expression(paste("Truck hours X ", 10^-5)))

# yscale <- c(1, 10^5, 1, 100000, 1, 1, 1, 1)
yscale <- rep(100000, 4)#, 10000, 10000)#, 1, 1, 1)
ftits <- list("Maximize Yields", "Minimize Carbon Loss", 
              "Minimize Biodiversity Loss", "Minimize Travel Cost")
# leg <- c("Converted")
yaxes <- list(seq(0, 16, 2), seq(0, 1200, 100), seq(0, 9, 1), 
              seq(0, 35, 5))

@@

### Figure 2 - yield-carbon efficiency frontier
```{r, eval = FALSE}
p <- data.frame(ybdc$both$params)
pare <- ybdc$both$optitab
p[, c("Y", "C", "BD" ,"COST")] <- round(p[, c("Y", "C", "BD" ,"COST")], 2)

# Y versus C tradeoffs only
yconly <- which(p[, "BD"] == 0 & p[, "COST"] == 0)

# p[yconly, ]
ycstats <- selected_impacts(yconly, fp(p_out, ybdc$both$bcode))
ycstats <- ycstats[, .(iter, conv_area, tot_C)]

# subset of sites to map
yc_ss <- c(1, 2, 6, 11, 21)
ycmins <- sapply(2:3, function(x) range(ycstats[[x]]))
(ycmins[2, 2] - ycstats[yc_ss, get("tot_C")]) / diff(ycmins[, 2]) 
round(ycstats[yc_ss, get("tot_C")] / ycmins[2, 2], 2)
# 1.00 0.69 0.46 0.41 0.39
round(ycstats[yc_ss, get("conv_area")] / ycmins[1, 1], 3)
# 1.000 1.006 1.034 1.057 1.129

# plot colors
colsyc <- colorRampPalette(c("red", "gold", "blue"))
colsyc <- colsyc(5)
colsyc[4] <- "skyblue"

png(fp(p_figures, "pareto_yc.png"), height = 7, width = 7, 
    units = "in", res = 300)
par(mar = c(6, 6, 3, 1))
plot(ycstats$conv_area / yscale[1], ycstats$tot_C / yscale[2], axes = FALSE, 
     xlab = "", ylab = "", pch = 16, col = "grey40", xlim = c(13.5, 15.5), 
     ylim = c(425, 1200), xaxs = "i", yaxs = "i", cex = 1.5)
points(ycstats$conv_area[yc_ss] / yscale[1], cex = 2,
       ycstats$tot_C[yc_ss] / yscale[2], pch = 16, col = colsyc)
# lines(ycstats$conv_area / yscale[1], ycstats$tot_C / yscale[2])
axis(1, at = seq(13.5, 15.5, 0.25), mgp = c(3, 0.5, 0), tcl = -0.2, 
     labels = sprintf("%.2f", seq(13.5, 15.5, 0.25)), las = 2, cex.axis = 1.5)
ys <- seq(400, 1200, 50)
# ys[-seq(2, 30, 3)]
yslab <- ys
# yslab[-seq(2, 32, 3)] <- ""
axis(2, at = ys, labels = yslab, las = 2, mgp = c(3, 0.5, 0), tcl = -0.2, 
     cex.axis = 1.5)
mtext(ylabs[1], side = 1, line = 4.75, cex = 1.5)
mtext(ylabs[2], side = 2, line = 3.5, cex = 1.5)
dev.off()

# maps for those sites, just for 0.25 increments
fnames <- imp_sorter(fp(p_out, ybdc$both$bcode), 
                     inds = yc_ss, fullnames = TRUE)
yc_r <- lapply(fnames, function(x) {  # x <- pure[1]
  DT <- cbind(fread(x), basedt[, .(x, y, convertible)])
  DTr <- dt_to_raster(DT, CRSobj)
})
yc_r2 <- lapply(yc_r, function(x) calc(x[[1:2]], sum))  # conv pixels
names(yc_r2) <- paste0("YC", 1:5)

# Plot maps
# plot(1:5, pch = 16, col = colsyc(5))
legtf <- rep(FALSE, 5)
for(i in 1:5) { # i <- 1
  par(bg = "transparent")
  imp_plot2(yc_r2[[i]], impacts = i1, fpath = p_figures, 
            fnm = paste0("ycplot_", i), crops = "", ftitle = "", 
            col = colsyc[i], legend = legtf[i], hold = FALSE, stats = FALSE, 
            cexscale = 0.4, marg = rep(0, 4))
}

# figure out overlaps between different pure objectives
pms2a <- expand.grid(rep(list(0:1), 5))[-1, ] 
pms2b <- pms2a[which(rowSums(pms2a) == 2 & pms2a$Var1 == 1), ]
pms2b$cl <- c("YC1", "YC2", "YC3", "YC4")
rownames(pms2b) <- 1:4

## proximity statistics
# pairwise overlaps
yc_over <- lapply(1:nrow(pms2b), function(x) {  # apply logic tests
  calc(stack(yc_r2[which(pms2b[x, ] == 1)]), sum)
})
names(yc_over) <- pms2b$cl

# Jaccard Index of overlaps
yc_over_a <- sapply(1:length(yc_over), function(x) { # x <- 4
  sapply(1:2, function(y) {  # y <- 3
    r <- yc_over[[x]] == y
    round(cellStats(r * pure_r[[1]]$convertible, sum), 1)
  })
})
pms2b$JS <- round(yc_over_a[2, ] / colSums(yc_over_a) * 100, 2)

# calculate nearest neighbor distance between each version, using spatstat 
# nncross
zam_owin <- owin(xrange = bbox(zambia)[1, ], yrange = bbox(zambia)[2, ],
                 unitname = "meter")
which1 <- function(x) x == 1  # selector function for r to xy
rsover_nn <- lapply(1:nrow(pms2b), function(x) {  # apply logic tests; x = 2
  ind <- which(pms2b[x, 1:5] == 1)
  rl <- yc_r2[ind]
  rxy <- lapply(rl, function(x) rasterToPoints(x, fun = which1))
  pps <- lapply(rxy, function(x) {
    ppp(x = x[, 1], y = x[, 2], window = zam_owin)
  })
  # reorder to find which has most points, to put that in as X
  reord <- sort(sapply(pps, function(x) x$n), decreasing = TRUE)
  ppnn <- nncross(pps[[names(reord)[1]]], pps[[names(reord)[2]]])
})
pms2b$NND <- round(sapply(rsover_nn, function(x) mean(x$dist))) / 1000

@@

### Figure 3

@@

cols_tr <- c(rgb(1, 0, 0), rgb(0, 0, 1), rgb(0, 0.75, 1), rgb(1, 0.75, 0))
# sctab <- do.call(rbind, scens) * 100
cx <- 0.7
imp_pct[, {
  png(fp(p_figures, "weight_impact5.png"), height = 4, width = 4, 
      units = "in", res = 300)
  plot(xwgts, conv_areap, type = "l", xlab = "", ylab = "", axes = FALSE, 
       ylim = c(0, 55), col = cols_tr[1])
  lines(xwgts, tot_Cp, col = cols_tr[2])
  lines(xwgts, cons_totp, col = cols_tr[3])
  lines(xwgts, tot_costp, col = cols_tr[4])
  axis(1, at = xwgts, labels = seq(0, 90, 10), cex = cx, cex.axis = cx, 
       line = -0.25, tcl = -0.2, mgp = c(1, 0.25, 0))
  axis(2, at = seq(0, 55, 5), las = 2, cex = cx, cex.axis = cx, line = -0.25, 
       tcl = -0.15, mgp = c(1, 0.25, 0))
  mtext("% Weight taken from Yield and divided", side = 1, line = 1, cex = cx)
  mtext("equally between Carbon & Biodiversity", side = 1, line = 1.75, 
        cex = cx)
  mtext("% Avoided Cost", side = 2, line = 1, cex = cx)
  legend("bottomright", 
         legend = c("Yield", "Carbon", "Biodiversity", "Travel cost"), 
         cex = cx, text.col = cols_tr, col = cols_tr, bty = "n", lty = 1, 
         inset = c(0, 0.25, 0, 0))
  dev.off()
}]

@@

### Figures 4 and 5

@@

@@

@@

@@

## Supplemental figures
### Overlap with Farm Blocks
```{r, eval = FALSE}
# Calculate area of overlaps between farmblocks and 
Y <- calc(mzsoytor, sum)
yfbr <- Y + fbr * 2
eqfbr <- toresr$eqwt + fbr * 2
fbrlist <- list(yfbr, eqfbr)

fb_over_a <- sapply(1:2, function(x) { # x <- 4
  sapply(1:3, function(y) {  # y <- 3
    r <- fbrlist[[x]] == y
    round(cellStats(r * pure_r[[1]]$convertible, sum), 1)
  })
})
fb_sim <- fb_over_a[3, ] / colSums(fb_over_a) * 100

@@

```{r, eval = FALSE, echo=FALSE}

@@

@@

```{r, eval = FALSE, echo = FALSE}
### Figures 2 & 3 (probably supplemental)
# Deprecated

# individual maps
# png(full_path(p_figures, "all-4-maps.png"), height = 7, width = 7, 
#      units = "in", res = 300)
# par(mfrow = c(2, 2))#, oma = c(0, 0, 0, 2))
# ftitles <- c("Yield", "Carbon", "Biodiversity", "Cost")
# legp <- c(TRUE, rep(FALSE, 3))
# for(i in 1:4) {
#   dtr <- calc(pure_r[[i]][[1:2]] * c(1, 2), sum)
#   imp_plot2(dtr, impacts = i1, fpath = p_figures, fnm = "all-4-maps", 
#             cexscale = 0.6, ftitle = ftitles[i], crops = c("maize", "soy"), 
#             stats = FALSE, hold = TRUE, legend = legp[i], marg = c(0, 0, 2, 0))
# }
# dev.off()

### 2016-05-05 Rmd/main-analysis.Rmd
Full paper revisions: main manuscript, fully revised, with edits and additions to SI methods and results.  New figure created (figures.Rmd), slight edit of loose code on main-analysis.Rmd

# Separate soy and maize impacts
cb <- c("Y" = 1, "C" = 0, "BD" = 0, "COST" = 0)
mzsoyto <- tradeoff_mod(prod_targ = targ, cbetas = cb, currprodmod = g)

@@

CRSobj <- CRS(mzto$inputs$sp$crs)
mzsoytor <- dt_to_raster(mzsoyto$conv, CRSobj)  # converges on same results

# Plot
i1 <- rbind(mzto$impacts, soyto$impacts)
basedt <- mzsoyto$inputs$mask
```
<a href="#top">Back to top</a>

>>>>

# Separate soy and maize impacts

# together
cb <- c("Y" = 1, "C" = 0, "BD" = 0, "COST" = 0)
mzsoyto <- tradeoff_mod(prod_targ = targ, cbetas = cb, currprodmod = g)

@@

CRSobj <- CRS(mzsoyto$inputs$sp$crs)
mzsoytor <- dt_to_raster(mzsoyto$conv, CRSobj)  # converges on same results

# Plot
# i1 <- rbind(mzto$impacts, soyto$impacts)
basedt <- mzsoyto$inputs$mask
```
<a href="#top">Back to top</a>
